---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
# install.packages('anivis', repos = c('https://animovement.r-universe.dev', 'https://cloud.r-project.org'))
```


# anivis
<!-- badges: start -->
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.17357778.svg)](https://doi.org/10.5281/zenodo.17357778)
[![R-CMD-check](https://github.com/animovement/anivis/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/animovement/anivis/actions/workflows/R-CMD-check.yaml)
[![anivis status
badge](https://animovement.r-universe.dev/badges/anivis)](https://animovement.r-universe.dev)
[![codecov](https://codecov.io/gh/animovement/anivis/graph/badge.svg?token=Pf5n3yzLzK)](https://codecov.io/gh/animovement/anivis)
<!-- badges: end -->

*An R package for visualizing movement data and diagnostics*

The primary aim of the _anivis_ package is to provide plotting methods for movement trajectories, diagnostic summaries, and calculated metrics.

## Installation

You can install the development version of *anivis* with:

```{r, eval=FALSE}
install.packages('anivis', repos = c('https://animovement.r-universe.dev', 'https://cloud.r-project.org'))
```

Once you have installed the package, you can load it with:

```{r, eval=FALSE}
library("anivis")
```

## Status
> **Warning**
>
> 🏗️ The package is currently in early development and the interface is subject to change. Feel free to play around and provide feedback.


## Citation {#citation}

If you enjoy the package, please make sure to cite it. If you find a bug, feel free to open an issue. 

To cite *anivis* in publications use:

```{r, eval=FALSE}
citation("anivis")
```
